%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.0 (5/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing
\hypersetup{
  colorlinks = true
}
\addbibresource{bibliography.bib} % Specify the bibliography file to include publications

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\rfoot{References available on request}

\begin{document}

\header{Arjun}{Menon}{} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{contact}
587 Bryson Ave.
Palo Alto, CA 94306
United States
+1 (412) 463 7895
~
\href{mailto:ajn.menon@gmail.com}{ajn.menon@gmail.com}
\href{http://www.arjunm.org}{http://www.arjunm.org}
\href{http://www.github.com/arjungm}{github.com/arjungm}
\href{https://www.linkedin.com/in/menonarjun}{linkedin: menonarjun}
\section{programming}
C++, Python, 
Java, MATLAB, LaTeX
\section{practical skills}
camera calibration,
pointcloud processing,
3D object modeling,
object recognition,
graph search,
motion planning,
trajectory control,
trajectory optimization,
kinematics \& dynamics modeling,
robot localization,
CAD (Inventor),
Lathe, Mill, Waterjet
\section{specific libraries}
ROS, PCL, SBPL,
MoveIt, OpenCV, 
CGAL, KDL
\section{languages}
English (fluent)
French (1 year)
German (1 year)
\section{honors}
NSCS, Tau Beta Pi, 
Gamma Beta Phi, 
Honors Program at GT
\section{interests}
First Lego League,
SciFi literature, 
Olympic Lifting,
Settlers of Catan,
and Backgammon
\end{aside}

%additional skills? Linux, LaTeX
\section{objective}
Seeking entry level position in growing global technology organization that utilizes my \\
academic qualifications and research experience. Technical interests are robotic planning and decision making, and software research and development.

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

\begin{entrylist}
%------------------------------------------------
\eduentry
{2012--2013}
{Masters {\normalfont of Robotics}}
{GPA 3.84/4.00}
{Carnegie Mellon University, Pittsburgh}
%------------------------------------------------
\eduentry
{2008--2012}
{Bachelors {\normalfont of Mechanical Engineering, Minor in Computer Science}}
{GPA 3.83/4.00}
{Georgia Tech, Atlanta}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\vspace{-2mm}
\section{experience}

\begin{entrylist}
%------------------------------------------------
\jobentry
{Jun 2014 - Present}
{SRI INTERNATIONAL}
{Palo Alto, California}
{Student Associate, Robotics}
{\begin{itemize}
\item Developed automated pipeline for batch recording robotic simulations.
\item Designed and will conduct user study to measure quality of robot motion plans.
\item Contributed patches to open source software for robotic motion planning, MoveIt.
\end{itemize}}
%------------------------------------------------
\jjobentry
{May 2013 - Dec 2013}
{SEARCH BASED PLANNING LABORATORY, CMU}
{Pittsburgh, Pennsylvania}
{Research Associate III}
{Graduate Student Researcher}
{Jan 2014 - Jun 2014}
{\begin{itemize}\item Developed dynamics-aware planner for PR2, for handling moving goals.
\item Created efficient search-heuristic for producing time-optimal robot motion.
\item Demonstrated planner for grabbing objects off conveyor without jerking them.
\item Incorporated online perception for realtime interactive demo of planning.
\end{itemize}}
%------------------------------------------------
\jobentry
{Aug 2012 - May 2013}
{PERSONAL ROBOTICS LABORATORY, CMU}
{Pittsburgh, Pennsylvania}
{Graduate Student Researcher}
{\begin{itemize}\item Built computational pipeline to link object detection with object discovery.
\item Programmatically generated novel object models from 3D data and images.
\item Demonstrated live robot performing perception and manipulation.
\item Developed an automatic camera and kinect self-calibration sequence.
\end{itemize}}
%------------------------------------------------
\jobentry
{May 2011 - May 2012}
{MOBILE ROBOT LABORATORY, GEORGIA TECH}
{Atlanta, Georgia}
{Undergraduate Researcher \& Lab Manager}
{\begin{itemize}\item Designed herding AI for robotic agents in prey-predator scenarios.
\item Created a finite state automata in multi-threaded simulation software, MissionLab.
\item Configured mobile robot software and hardware for experimentation.
\end{itemize}}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------
\vspace{-2mm}
\section{publications}

\printbibsection{article}{article in peer-reviewed journal} % Print all articles from the bibliography

\printbibsection{book}{books} % Print all books from the bibliography

\begin{refsection} % This is a custom heading for those references marked as "inproceedings" but not containing "keyword=france"
\nocite{*}
\printbibliography[sorting=chronological, type=inproceedings, notkeyword={france}, heading=none]
\end{refsection}

\begin{refsection} % This is a custom heading for those references marked as "inproceedings" and containing "keyword=france"
\nocite{*}
\printbibliography[sorting=chronological, type=inproceedings, title={local peer-reviewed conferences/proceedings}, keyword={france}, heading=subbibliography]
\end{refsection}

\printbibsection{misc}{other publications} % Print all miscellaneous entries from the bibliography

\printbibsection{report}{research reports} % Print all research reports from the bibliography
%----------------------------------------------------------------------------------------
\end{document}
